Design and Implementation of Probabilistic Programming Language Anglican

### 2017-03-14 paper/paper.tex
better placed figures

\begin{figure}
    \centering
    \includegraphics[trim={6pt 12pt 0 12pt},scale=0.6]{same-customer-time.pdf}
    \caption{Arrival time distribution for a single customer.}
    \label{fig:dist-same}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[trim={6pt 12pt 0 12pt},clip,scale=0.6]{different-customers-times.pdf}
    \caption{Arrival time distributions for two customers.}
    \label{fig:dist-diff}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[trim={0pt 12pt 0 12pt},scale=0.6]{same-customer-time.pdf}
    \caption{Arrival time distribution for a single customer.}
    \label{fig:dist-same}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[trim={0pt 12pt 0 12pt},clip,scale=0.6]{different-customers-times.pdf}
    \caption{Arrival time distributions for two customers.}
    \label{fig:dist-diff}
\end{figure}
